Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
Cahngement sur les auteurs (à finir)
Correction de fautes

\title{Adaptative neigbouring methods applied to telephonic base stations}
\author{Paul MÉHAUD, Brendan SÉVELLEC}

@@

    This database is updated every quarter. For instance, the own we used was published on 28th March 2024 \cite{main_database_hist}.

@@

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} &You can 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

>>>>

\title{Adaptative neigbouring methods applied to telephonic base stations}
\author{\IEEEauthorblockN{Paul MÉHAUD}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
paul.mehaud@insa-rouen.fr}\\
\and
\IEEEauthorblockN{Brendan SÉVELLEC}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
brendan.sevellec@insa-rouen.fr}}

@@

    This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.

@@

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}
